Dirichlet discretization of Neumann problems

### 2020-01-07 paper_lap/06num.tex
conclusion and minor edits

\section{Numerical results}
\subsection{Accuracy}
In this section, we demonstrate the accuracy of the proposed numerical method (both in the {\it weak} sense 
described above, 
as well as in the classical sense after sufficiently many re-solves) on the triangular domain shown below. 
The reference solution for each of the examples is computed using a discretization with
a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-150}$ times
the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). 
\begin{rem}
Though $2^{-150}$ is significantly smaller than machine precision, the matrix entries corresponding to the
corner interactions can be computed accurately by translating the corners to the origin when 
computing interactions of nearby points.
\end{rem} 
\begin{rem}
Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
machine precision 
($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel size (i.e. the size of the 
panel closest to the corner) to be of size $2^{-100}.$ However, it is not true that the value of the density is 
accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$.

It is well-known that a smallest panel size of $2^{-100}$ is sufficient to resolve the density corresponding
to solutions of the Neumann problem in order to obtain full machine precision ($\sim 1.11 \times 10^{-16}$) for the solution anywhere in the volume sufficiently far from the corner.
However, it is not true that the value of the density is accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$. 
\end{rem}
In these examples, the solutions are computed via dense linear solves.

The potential at target locations which are more than 1 panel length away is the inner product of the 
density with a smooth function. For a target location $\boldsymbol{y}$, we compute the solution via the formula,
\begin{equation}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
\end{equation}
In figure~\cref{fig:far-field}, we compute the error in the solution at target
locations in the volume for the right hand side given by
\begin{equation}
f(\bx) = 
\end{equation}

Another example of weak quantity is the polarization tensor associated with a domain. This requires the solution of the
exterior problems with boundary data $f_{1} = \bnu_{1}$ or $f_{2} = \bnu_{2}$. Let $\sigma_{1}$ and $\sigma_{2}$ denote
the corresponding solutions. The polarization tensor can be expressed in terms of the solutions $\sigma_{1}$ and $\sigma_{2}$
as
\begin{equation}
P = \begin{bmatrix}
\int_{\Gamma} x_{1} \sigma_{1}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{1}(\bx) dS_{\bx} \\
\int_{\Gamma} x_{1} \sigma_{2}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{2}(\bx) dS_{\bx} 
\end{bmatrix}
\end{equation}
The polarization tensor as computed by the reference solution, and the error in computation using the adjoint method
are given by
\begin{equation}
P = \begin{bmatrix}
\end{bmatrix} \, , \quad \text{Error} = 
\begin{bmatrix} 
\end{bmatrix}
\end{equation}

In order to demonstrate the capability to obtain the true density at the corner panels, we  apply the procedure
discussed in~\cref{sec:resolve} iteratively, and compare the obtained density with the reference density after 20,40,60, and
80 iterations of resolves in the vicinity of one of the corners. The reference density and the errors are shown in ~\cref{fig:dens-error}.

After re-solving the density, we also compute the solution at target locations on a tensor product polar grid, where the grid
is exponentially spaced in the radial direction and equispaced in the angular direction. For target locations
close to panels which are not at the corner, we use adaptive integration in order to resolve the near-singular behavior of
the kernel for accurate computation of the integrals. For target locations close to the corner panel, since we do not have
the capability to interpolate the density, we use the underlying smooth quadrature rules for computing their contribution. 
The reference solution and the errors are demonstrated in~\cref{fig:vol-plot}.
\subsection{Performance}
In this section, we demonstrate the performance of the solver of two large domains. We solve scattering problems in the
exterior of a magnetron like region, and the maple leaf. The right hand side is the potential due to a collection of charges in the exterior of the region, and we impose that

>>>>

\section{Numerical results}
\subsection{Accuracy}
In this section, we demonstrate the accuracy of the proposed numerical method (both in the {\it weak} sense 
described above, 
as well as in the classical sense after sufficiently many re-solves) on the triangular domain shown below. 
The reference solution for each of the examples is computed using a discretization with
a graded mesh in the vicinity of the corners, where the smallest panel at the corner is $2^{-150}$ times
the length of the first macroscopic panel away from the corner (see~\cref{fig:dom}). 
\begin{rem}
Though $2^{-150}$ is significantly smaller than machine precision, the matrix entries corresponding to the
corner interactions can be computed accurately by translating the corners to the origin when 
computing interactions of nearby points.
\end{rem} 
\begin{rem}
Simple arguments from complex analysis show that when using graded meshes, in order to obtain full 
machine precision 
($\sim 1.11 \times 10^{-16}$) for solutions of the Neumann problem at any point in the interior 
at least $10^{-16}$ away from a corner, it suffices to choose the smallest panel (i.e. the size of the 
panel closest to the corner) to be of size $2^{-100}.$ However, resulting values of the density will not be 
accurate to machine precision at all nodes. In fact the quality
of the density deteriorates as one approaches the corner. Thus, in order to obtain accurate point values
of the density to machine precision at all points which are at least $2^{-100}$ away from the corner, we use a smallest
panel size of $2^{-150}$. 
\end{rem}
In these examples, the solutions are computed via dense linear solves.

The potential at target locations which are sufficiently far from the boundary (i.e. at least one panel length away from 
every panel) is the inner product of the 
density with a smooth function and hence can be computed accurately without re-solving. For a target 
location $\boldsymbol{y}$, we compute the solution via the formula,
\begin{equation}
u(\by) = \int_{\Gamma} G(\bx,\by) \sigma(\bx) dS_{\bx} \approx \sum_{i=1}^{N}  G(\gamma(s_{i}),\by) \sigma_{i} \sqrt{w_{i}}
\end{equation}
In figure~\cref{fig:far-field}, we compute the error in the solution at target
locations in the volume for the right hand side given by
\begin{equation}
f(\bx) = 
\end{equation}

Another example of a ``weak quantity'' is the polarization tensor associated with a domain. This requires the solution of the
exterior problems with boundary data $f_{1} = \bnu_{1}$ or $f_{2} = \bnu_{2}$. Let $\sigma_{1}$ and $\sigma_{2}$ denote
the corresponding solutions. The polarization tensor can be expressed in terms of the solutions $\sigma_{1}$ and $\sigma_{2}$
as
\begin{equation}
P = \begin{bmatrix}
\int_{\Gamma} x_{1} \sigma_{1}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{1}(\bx) dS_{\bx} \\
\int_{\Gamma} x_{1} \sigma_{2}(\bx) dS_{\bx} & \int_{\Gamma} x_{2} \sigma_{2}(\bx) dS_{\bx} 
\end{bmatrix}
\end{equation}
The polarization tensor as computed by the reference solution, and the error in computation using the adjoint method
are given by
\begin{equation}
P = \begin{bmatrix}
\end{bmatrix} \, , \quad \text{Error} = 
\begin{bmatrix} 
\end{bmatrix}
\end{equation}

In order to demonstrate the accuracy of the corner re-solving approach in obtaining the true density at the corner panels, we  apply the procedure
discussed in~\cref{sec:resolve} iteratively, and compare the obtained density with the reference density after 20,40,60, and
80 iterations of resolves in the vicinity of one of the corners. The reference density and the errors are shown in ~\cref{fig:dens-error}.

After re-solving the density, we also compute the solution at target locations on a tensor product polar grid, where the grid
is exponentially spaced in the radial direction and equispaced in the angular direction. For target locations
close to panels which are not at the corner, we use adaptive integration in order to resolve the near-singular behavior of
the kernel for accurate computation of the integrals. For target locations close to the corner panel, since we do not have
the capability to interpolate the density, we use the underlying smooth quadrature rules for computing their contribution. 
The reference solution and the errors are demonstrated in~\cref{fig:vol-plot}.
\subsection{Performance}
In this section, we demonstrate the performance of the solver on two large domains. We solve scattering problems in the
exterior of a ``broken wheel'' region, and the maple leaf. The right hand side is the potential due to a collection of charges in the exterior of the region, and we impose that

### 2020-01-07 paper_lap/manuscript.tex
conclusion and minor edits

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
In this section, we demonstrate that for a panel which is away from the corner, which is discretized using $M$ Gauss-Legendre nodes, where the solution is computed using the adjoint of a Dirichlet discretization, the density can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]$ denote an arc-length parameterization of the boundary.
Let $\gamma([s_{1},s_{2}])$ be a panel discretized using $M$ Gauss-Legendre nodes be such that if $r_{0}$ denotes
the distance to the closest corner on the particular edge, the length of the panel $L_{0}<r_{0}/2$, i.e. the panel
is separated from the nearest corner by at least two times its own length. Further assume that no point on the boundary $\Gamma$ which is not on the same edge as as $\gamma([s_{1},s_{2}])$ is contained in some $\rho-$Bernstein ellipse
corresponding to the line segment $\gamma([s_{1},s_{2}])$ with $\rho>1$. Furthermore suppose that all of the panels away from the corner and not on the edge containing the segment $\gamma([s_{1},s_{2}])$ are such that any point on $\gamma([s_{1},s_{2}])$ is not contained in their $\rho-$ Bernstein ellipse.
Both of these assumptions can always be met by choosing sufficiently small panels away from the corners. Finally 
assume that all panels at any corner $r_{c}$ are such that any point on $\gamma([s_{1},s_{2}])$ is at least $2r_{c}$ 
away from the corner vertex. Under all of these assumptions, it can be shown that the accuracy in computing the
Legendre coefficients of the density corresponding to the Neumann problem, is the same as the accuracy
of a related Dirichlet problem where the boundary data is resolved with controlled error on the given discretization.

Let $A$ denote the operator corresponding to interior Dirichlet problem using a double layer potential. Let $g$ denote the
right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution. Let $f$ be a Legendre polynomial of
degree $n$ scaled to the panel $\gamma_{[s_{1},s_{2}]}$ and $0$ everywhere else. Then
\begin{equation}
\left<\sigma, f \right> = \left< (A^{T})^{-1} g, f\right> = \left< g, A^{-1} f \right> = <g, \sigma_{f}> \, ,
\end{equation}
where $\sigma_{f}$ is the solution of the interior Dirichlet problem with boundary data $f$ using a double layer potential.

Using~\cref{lem_adjm}, the above statement implies that the error in computing the $n$ Legendre coefficient of
the density for the Neumann problem, is the same as error in computing the solution of a Dirichlet problem with 
data given by a Legendre polynomial on the same edge.  This seems problematic since the right hand side
is not smooth, however, in the special case of polygonal domains, this problem is alleviated since the kernel corresponding
to the double layer potential is identically zero on line segments.

>>>>

\section{Strong approximation of density away from corner panels}
\label{sec:appb}
In this section, we demonstrate that for a panel which is sufficiently far from the corner and  discretized using $M$ Gauss-Legendre nodes, the density computed using the adjoint of a Dirichlet discretization can be interpolated 
accurately at any point on the panel. As before let $\Omega$ denote a polygonal domain with boundary $\Gamma$. Let
$L$ denote the length of the boundary, and let $\gamma: [-L/2,L/2]$ denote an arc-length parameterization of the boundary.
Let $\gamma([s_{1},s_{2}])$ be a panel discretized using $M$ Gauss-Legendre nodes be such that if $r_{0}$ denotes
the distance to the closest corner on the particular edge, the length of the panel $L_{0}<r_{0}/2$, i.e. the panel
is separated from the nearest corner by at least two times its own length. Further assume that no point on the boundary $\Gamma$ which is not on the same edge as as $\gamma([s_{1},s_{2}])$ is contained in some $\rho-$Bernstein ellipse
corresponding to the line segment $\gamma([s_{1},s_{2}])$ with $\rho>1$. Furthermore suppose that all of the panels away from the corner and not on the edge containing the segment $\gamma([s_{1},s_{2}])$ are such that any point on $\gamma([s_{1},s_{2}])$ is not contained in their $\rho-$ Bernstein ellipse.
Both of these assumptions can always be met by choosing sufficiently small panels away from the corners. Finally 
assume that all panels at any corner $r_{c}$ are such that any point on $\gamma([s_{1},s_{2}])$ is at least $2r_{c}$ 
away from the corner vertex. Under all of these assumptions, it can be shown that the accuracy in computing the
Legendre coefficients of the density corresponding to the Neumann problem, is the same as the accuracy
of a related Dirichlet problem where the boundary data is resolved with controlled error on the given discretization.

Let $A$ denote the operator corresponding to interior Dirichlet problem using a double layer potential. Let $g$ denote the
right hand side for the Neumann problem, let $\sigma$ denote the corresponding solution. Let $f$ be a Legendre polynomial of
degree $n$ scaled to the panel $\gamma_{[s_{1},s_{2}]}$ and $0$ everywhere else. Then
\begin{equation}
\left<\sigma, f \right> = \left< (A^{T})^{-1} g, f\right> = \left< g, A^{-1} f \right> = \langle g, \sigma_{f}\rangle \, ,
\end{equation}
where $\sigma_{f}$ is the solution of the interior Dirichlet problem with boundary data $f$ using a double layer potential.

Using~\cref{lem_adjm}, the above statement implies that the error in computing the $n$ Legendre coefficient of
the density for the Neumann problem is the same as the error in computing the solution of a Dirichlet problem with 
data given by a Legendre polynomial on the same panel.  %This seems problematic since the right hand side
%is not smooth, however, in the special case of polygonal domains, this problem is alleviated since the kernel corresponding
%to the double layer potential is identically zero on line segments.
